An SMT-based Approach to Coverability Analysis

### 2014-02-05 paper/workspace/sec_preliminaries.tex
Outline for preliminaries.

\begin{verbatim}
* Petri net:
 N = (S, T, E, M0), where
     S : places
     T : transitions
     E : edges
     M0: initial marking

* Property:
 P, linear arithmetic formula
\end{verbatim}

>>>>

\begin{verbatim}
* Petri net: definition
 N = (S, T, E, M0), where
     S : places
     T : transitions
     E : edges
     M0: initial marking

* Marking: definition

* Visual representation of Petri Nets: description, example

* Property P: safety property expressed over linear arithmetic formulas.

* Linear arithmetic formula: examples

* N \models P: definition

* Whatever you believe should be defined for the paper.
\end{verbatim}
